% ATS-friendly one-page resume
% Compile: pdflatex Devyanshu_Jadon_Resume.tex
\documentclass[10.5pt,a4paper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black,
  pdfauthor={Devyanshu Jadon},
  pdftitle={Devyanshu Jadon -- Resume}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{
  leftmargin=1.15em,
  itemsep=2pt,
  topsep=3pt,
  parsep=0pt,
  partopsep=0pt
}

\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\vspace{-2pt}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\newcommand{\roleline}[3]{%
  \textbf{#1} \hfill #3\\[-0.5pt]
  \textit{#2}\\[2pt]
}

\begin{document}

% ---------- HEADER ----------
\begin{center}
  {\LARGE\bfseries Devyanshu Jadon}\\[3pt]
  AI and Backend Engineer\\[3pt]
  \href{mailto:jadon.devyanshu@gmail.com}{jadon.devyanshu@gmail.com}
  $\cdot$ India (Remote)\\[2pt]
  \href{https://github.com/devyanshujadon}{github.com/devyanshujadon}
  $\cdot$
  \href{https://linkedin.com/in/devyanshu-jadon}{linkedin.com/in/devyanshu-jadon}
  $\cdot$
  \href{https://devyanshu.com}{devyanshu.com}
\end{center}

% ---------- SUMMARY ----------
\section{Summary}
AI and backend engineer focused on production LLM systems, retrieval pipelines, and reliable APIs. Build intelligent features for enterprise use and ship end-to-end products---from a lightweight LLM orchestration library to a full feedback platform. Comfortable across Python, TypeScript, RAG architectures, and cloud infrastructure.

% ---------- SKILLS ----------
\section{Skills}
\textbf{Languages:} Python, TypeScript, JavaScript, Go\\[2pt]
\textbf{AI / ML:} Large Language Models (LLMs), Retrieval-Augmented Generation (RAG), LangChain, LangGraph, TensorFlow, PyTorch\\[2pt]
\textbf{Backend \& APIs:} FastAPI, Node.js, Flask, Pydantic, SQLAlchemy, REST API design\\[2pt]
\textbf{Frontend:} Next.js, React, TypeScript\\[2pt]
\textbf{Data \& Infrastructure:} PostgreSQL, MongoDB, Redis, Docker, Kubernetes, AWS\\[2pt]
\textbf{Practices:} Production system design, database design, cloud architecture, machine learning integration

% ---------- EXPERIENCE ----------
\section{Experience}

\roleline{AI Engineer}{Tudip Technologies}{2025 -- Present}
\begin{itemize}
  \item Design and implement intelligent data pipelines and LLM integrations for enterprise applications.
  \item Build production-ready retrieval and inference workflows that connect models to reliable backend services.
  \item Partner with product and engineering teams to ship AI features that are maintainable, observable, and operable in production.
\end{itemize}

\vspace{5pt}
\roleline{IBM Z Ambassador}{IBM}{2020 -- 2022}
\begin{itemize}
  \item Advocated enterprise mainframe and Z Systems technologies through community engagement and technical outreach.
  \item Facilitated technical workshops and knowledge-sharing sessions for students and early-career developers.
\end{itemize}

% ---------- PROJECTS ----------
\section{Projects}

\roleline{LoomKit}{Python LLM orchestration library}{2025}
\href{https://loomkit.vercel.app/}{loomkit.vercel.app}
$\cdot$ \texttt{pip install loomkit}
\begin{itemize}
  \item Built a lightweight, swappable LLM orchestration core using a Provider Protocol so backends can be exchanged without inheritance or registration.
  \item Defined a minimal Message, Response, and Usage surface for chat-style generation while keeping the core package zero-dependency.
  \item Shipped Gemini support as an optional extra; designed the API to layer streaming, tools, retries, and agents later without breaking call sites.
\end{itemize}

\vspace{5pt}
\roleline{FeedFr}{Full-stack feedback product}{2025}
\href{https://feedfr.com}{feedfr.com}
$\cdot$ Next.js, TypeScript, PostgreSQL
\begin{itemize}
  \item Built and shipped a live product for collecting, prioritizing, and closing the loop on user feedback without enterprise overhead.
  \item Implemented public feedback boards with voting, product roadmaps, changelogs, and an embeddable in-product capture widget.
  \item Delivered the full stack end to end---auth, data model, product surfaces, and a free-to-paid tier---using Next.js, TypeScript, and PostgreSQL.
\end{itemize}

% ---------- EDUCATION ----------
\section{Education}

\textbf{Bachelor of Technology (B.Tech), Computer Science and Engineering (CSE)} \hfill 2020 -- 2024\\
\textit{Bansal Institute of Science and Technology, Bhopal}

\end{document}
